Source Summaries

### 2020-04-25 paper/sourceSummaries/summary10.tex
summary 10 initial commit

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{Experimental} {Design}}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{kirk2012experimental}

@@

\noindent
Author Roger E. Kirk explains in depth the process for designing experiments that yield the most significant and meaningful results. He builds off of work done by Sir Ronald Fisher in the early 20th century, as well as touches on some items to be wary of when undertaking this process.

@@

\noindent
This paper aims to effectively use scientific theory to aid researchers in properly exploring their research topics.

@@

\noindent
The author analyzes numerous types of experimental design with two main goals the mind. The first being to establish a causal connection between the independent and dependent variables, and the second being to extract the maximum amount of information with the minimum expenditure of resources.

@@

\noindent
The author presents no clear comparison data as findings to his readers, and instead leaves the decision up to his readers to interperet his data however they see fit for the benefit of their experiment.

@@

\noindent
In this section of his reasearch, the author suggests no future directions to continue his work.
